Probabilistic Model of Bilateral Lymphatic Spread in Head and Neck Cancer

### 2024-08-20 manuscript.qmd
add upstream prevalence plot

>>>>

### Influence of Upstream Involvement on Contralateral Metastasis

![The influence of the upstream LNL II's involvement on the prevalence of contralateral level III for the four combinations of tumor lateralization (lateralized or extending over midline) and T-ctageory (early or advanced). Our model predictions (histograms) are plotted against the observations in the data (beta posteriors).](figures/fig_model_prevalences_upstream.svg){#fig-model-prevalences-upstream}

@Fig-model-prevalences-upstream illustrates how rarely the contralateral LNL III harbors metastases when its upstream level II is healthy. Also, the model can capture this correlation rather well, with the exception of early T-category tumors that extend over the mid-sagittal line. As in @fig-model-prevalences-overall and @fig-model-prevalences-with-ipsi, these cases are relatively rare resulting in a broad distribution over the true prevalence.
